Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-13 examples.tex
+
subseteq

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred)  \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \textsf{ pte\_addr} \; \ast }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \textsf{ pte\_addr} \; \ast }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \;\ast}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace} (<[\vaddr:=\texttt{fpaddr}]> \theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \; \ast}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace} (<[\vaddr:=\texttt{fpaddr}]> \theta,\gammaPred) \ast \vaddr \mapsto_{\textsf{vpte}}\; \qfrac \;\fpaddr \textsf{ wzero 64}}_{\rtv}$

@@

  \caption{Specification and proof of distilled code for mapping a new page with $\textsf{wpd\_def }_{\rtv}$}

@@

Finally, we can insert $\vaddr$ into the ghost page-table-walk summarization map ($\theta$) to change its state from unmapped ($\ulcorner \theta \;!!\;\vaddr = \texttt{None}\urcorner$ in Specification Line 30) to mapped, and construct virtual-pointsto for $\sumwalkabs\vaddr\qfrac\fpaddr$ with fragmental ownership of

After storing $\textsf{pte\_addr}$
%\todo[inline]{emphasize the write to the L1 page table is validated by the fact that the identity mapping exists}
\subsection{Unmapping a Page}
The reverse operation, unmapping a designated page that is currently mapped, is pleasingly the reverse: by flipping the entry back to an invalid entry, full ownership of the updated entry reverts back to the now-invalid cell of the L1 table.

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast [\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,\gammaPred') \ast \texttt{Pother})}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv) \ast [\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,\gammaPred') \ast \texttt{Pother})}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast [\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,\gammaPred') \ast \texttt{Pother}) }_{\rtv}$

@@

$\specline{ [\rtv](\texttt{Pcurrent}) \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred') \ast \texttt{Pother}}_{\rtv'+56}$

>>>>

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m)  \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \textsf{ pte\_addr} \; \ast }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \textsf{ pte\_addr} \; \ast }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \;\ast}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace} (<[\vaddr:=\texttt{fpaddr}]> \theta,m) \ast}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace} (<[\vaddr:=\texttt{fpaddr}]> \theta,m) \ast \vaddr \mapsto_{\textsf{vpte}}\; \qfrac \;\fpaddr \textsf{ wzero 64}}_{\rtv}$

@@

  \caption{Specification and proof of distilled code for mapping a new page with $\textsf{wpd\_def }_{\rtv}$ with a fixed namespace $\gammaPreds$ and a global map of address-spaces $m$  }

@@

Finally, we can insert $\vaddr$ into the ghost page-table-walk summarization map ($\theta$) to change its state from unmapped ($\ulcorner \theta \;!!\;\vaddr = \texttt{None}\urcorner$ in Specification Line 30) to mapped (Specification Line 33) by Iris' ghost-map update ($\sqsubseteq$), and construct virtual-pointsto $\vaddr \mapsto_{\textsf{vpte}}\; \qfrac \;\fpaddr \textsf{ wzero 64}$ (Specification Line 36) with $\sumwalkabs\vaddr\qfrac\fpaddr$ obtained from ghost page-table-walk insertions, $\sumapaces\rtv\delta$ from unfolding the definition of $\mapsto_{\textsf{vpte}}$ in Specification Line 18, and $\fpaddr \mapsto_{\textsf{p}} \textsf{wzero 64}$ in Specification Line 34. fragmental ownership of 
\subsection{Unmapping a Page}
The reverse operation, unmapping a designated page that is currently mapped, is pleasingly the reverse: by flipping the entry back to an invalid entry, full ownership of the updated entry reverts back to the now-invalid cell of the L1 table.

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast [\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,m) \ast \texttt{Pother})}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast [\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,m) \ast \texttt{Pother})}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast [\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,m) \ast \texttt{Pother}) }_{\rtv}$

@@

$\specline{ [\rtv](\texttt{Pcurrent}) \ast \mathcal{I}\texttt{ASpace}(\theta,m) \ast \texttt{Pother}}_{\rtv'+56}$
